%-------------------------------------------------------------------------------
% Titlepage
%-------------------------------------------------------------------------------
\WaterMark[0.15\paperwidth]{UScrest-WM} 
\TitlePage

%-------------------------------------------------------------------------------
% Declaration page
%-------------------------------------------------------------------------------
\chapter{Declaration}
By submitting this dissertation electronically, I declare that the entirety of the work contained therein is my own, original work, that I am the sole author thereof (save to the extent explicitly otherwise stated), that reproduction and publication thereof by \mbox{Stellenbosch University} will not infringe any third party rights and that I have not \mbox{previously} in its entirety or in part submitted it for obtaining any qualification. \\ \\

\noindent
\begin{tabular}{@{}ll}
\textbf{Date:} & November 8, 2019 \\ 
\textbf{Name:} & Dumisile Lumkwana \\ 
\end{tabular}

\vspace*{\fill}
\begin{center}
Copyright $\textcopyright$ Stellenbosch University \\
All rights reserved.
\end{center}

%-------------------------------------------------------------------------------
% Abstract
%-------------------------------------------------------------------------------
\chapter{Abstract}

\textit{Introduction} - Alzheimer’s disease (AD) is a progressive neurodegenerative disorder characterized by multiple cognitive deficits. The neuropathology of AD is underpinned by two molecular hallmarks; intracellular protein aggregates known as neurofibrillary tangles (NFTs), composed of hyper-phosphorylated Tau and extracellular amyloid beta (A$\beta$) plaques, composed of A$\beta$ peptides derived from the amyloid precursor protein (APP). Both of these occur as a result of an imbalance in proteostasis, leading to neuronal toxicity. Although, we have advanced our understanding of the molecular machinery that regulates the rate of protein degradation through autophagy at basal levels and increasingly so the many aspects of its dysfunction in AD, the deviation of autophagic activity from basal levels and its change during disease pathogenesis in neuronal tissue remains largely unclear. Over the recent years, substantial progress has been made in modulating autophagy using pharmacological agents \textit{in vitro} and \textit{in vivo} and mounting evidence points towards autophagy modulation using pharmacological agents as one of the major therapeutic strategies for neurodegenerative diseases. Although spermidine and rilmenidine both enhance autophagy, the relationship between autophagy activity, the extent of protein clearance and cell death onset remains unclear. Moreover, the impact of their concentration on autophagic flux and subsequent protein clearance as well as neuronal toxicity is unclear. Therefore, this study aimed to unravel the impact of using a high and low concentration of spermidine and rilmenidine on autophagic flux, neuronal toxicity and protein clearance using distinct neuronal injury model systems. 

\textit{Methods} - Murine hypothalamus-derived GT1-7 neuronal cells and the mouse neuroblastoma (N2a) cell line stably expressing Swedish double mutation APP695 (Swe) associated with AD pathology were used. GT1-7 cells transfected with mRFP-GFP-LC3 and GFP-LC3-RFP-LC3$\Delta$G were treated with a low and high concentration of spermidine and rilmenidine in the absence and presence of saturating concentrations of bafilomycin, after which the autophagic flux profile was characterized, assessing cellular viability, autophagosome pool, autolysosome pool, autophagosome flux, transition time, p62 puncta and autophagic vacuoles. Cellular viability assays, western blotting, fluorescence microscopy, transmission electron microscopy and correlative light and electron microscopy linked to quantitative morphometric analysis was performed. In addition, potential protective effects of a low and high concentration of spermidine and rilmenidine were assessed in a paraquat (PQ)-induced neuronal toxicity model and in an APP over-expression model. Cellular viability, ROS damage, cell death onset and autophagic activity were assessed in the PQ-induced toxicity model, while in the APP model, cellular viability and protein clusters were assessed and quantified using cellular viability assays and single molecule imaging, i.e. direct Stochastic Optical Reconstruction Microscopy (d-STORM). Moreover, a Correlative Light and Electron Microscopy (CLEM) method was developed and implemented to morphometrically assess the effects of a low and high concentration of spermidine on the localization of autophagosomes in 3 dimensions. Finally, potential protective effects of spermidine at two distinct concentrations were assessed using transgenic mice expressing GFP-LC3, treated with PQ to induce neuronal toxicity associated with neurodegeneration.

\textit{Results} - Our results indicate a concentration-dependent effect of spermidine and rilmenidine on autophagic flux with the detected change in flux depending on the specificity and sensitivity of the method employed.  In addition, in the \textit{in vitro} model of PQ-induced toxicity, our results revealed that spermidine at a low concentration and not a high concentration protected against cell toxicity, ROS damage, cell death as well as microtubule destabilization. To our surprise, both concentrations of rilmenidine failed to protect against ROS damage and cell death and also failed to robustly upregulate autophagy in the same model.  Moreover, in the \textit{in vitro} model of neuronal toxicity induced by APP over-expression, our results showed that both concentrations of spermidine and rilmenidine protected against cytotoxicity. Here, spermidine at a low concentration effectively cleared APP clusters and reduced their size, especially after 48 h of APP over-expression, while rilmenidine, reduced the number and size of APP clusters in a concentration-dependent manner at the same time point.  
Taken together, the \textit{in vitro} results reveal a concentration-dependent effect, that is cell type and injury specific, impacting autophagy and cell death control. Moreover, we have successfully implemented a 3D CLEM protocol and revealed that spermidine, in combination with BafA1 decreases autophagosome volume while increasing their surface area in a concentration-dependent manner. Lastly, \textit{in vivo}, our results reveal that PQ-induced toxicity impacts the brain regions differentially, with the hippocampus being highly susceptible to PQ-induced injury followed by the cortex. Moreover, our results show that both dosages of spermidine robustly protected against oxidative stress, neuronal damage, microtubule destabilization, and upregulated autophagy, in the hippocampus and cortex. However, the low dose of spermidine resulted in more enhanced protection, although, autophagy was here region-specifically upregulated in a manner dependent on the dose utilized, with the higher dose of spermidine increasing LC3-II in the hippocampus, and the lower dose increasing LC3-II in the cortex. 

\textit{Conclusion} - Our results indicate the critical importance of using multiple tools to assess autophagy and show that a concentration-dependent effect of the two selected drugs on autophagic flux exists. In addition, we provide evidence of the distinct, context-dependent protective roles of spermidine and rilmenidine in an \textit{in vitro} model of APP over-expression as well as the protective roles of spermidine using \textit{in vitro} and \textit{in vivo} models of PQ-induced neuronal toxicity. These results suggest that firstly administration of spermidine may represent a favourable therapeutic strategy for the treatment of AD and secondly, concentration / flux screening may be more critical for optimal autophagy control than previously thought. Future studies, using an \textit{in vivo} model over-expressing APP are warranted to further verify the protective effects of spermidine, to foster clinical translation and therapeutic intervention in neurodegenerative disorders. 

\chapter{Opsomming}
\textit{Inleiding} – Alzheimer se siekte (AS) is 'n progressiewe neurodegeneratiewe versteuring wat gekenmerk word deur veelvuldige kognitiewe tekorte. Die neuropatologie van AS word gekenmerk deur twee molekul{\^e}re eienskappe; intrasellul{\^e}re prote{\"i}enaggregate bekend as neurofibrill{\^e}re knope (NFK), saamgestel uit hiper-gefosforileerde Tau, en ekstrasellul{\^e}re amilo{\"i}ede beta (A$\beta$) plake, saamgestel uit Ab-peptiede wat afkomstig is van die amilo{\"i}ede voorloperprote{\"i}en (AVP). Beide kom voor as gevolg van 'n wanbalans in proteostase, wat lei tot neuronale toksisiteit. Alhoewel ons begrip van die molekul{\^e}re masjinerie wat die tempo van prote{\"i}endegradasie deur outofagie op basale vlakke reguleer gevorder het en dan toenemend ook die vele aspekte van AS wanfunksie, bly die afwyking van outofagiese aktiwiteit vanaf die basale vlakke en die verandering tydens siekte patogenese in neuronale weefsel grootliks onduidelik. In die afgelope paar jaar is aansienlike vordering gemaak met die modulering van outofagie met behulp van farmakologiese middels \textit{in vitro} en \textit{in vivo}, en die toenemende bewyse dui daarop dat outofagiese modulering deur middel van farmakologiese middels een van die belangrikste terapeutiese strategie{\"e} vir neurodegeneratiewe siektes is. Alhoewel spermidien en rilmenidien beide outofagie verhoog, bly die verband tussen outofagie-aktiwiteit, die omvang van prote{\"i}enopruiming en die aanvang van seldood nie duidelik nie. Verder, die impak van hul konsentrasie op outofagiese stroom en daaropvolgende prote{\"i}enopruiming, sowel as op neuronale toksisiteit, is onduidelik. Daarom was die oogmerk van hierdie studie om die impak van beide ho{\"e} en lae konsentrasies spermidien en rilmenidien op outofagiese stroom, neuronale toksisiteit en prote{\"i}enopruiming met behulp van verskillende neuronale beseringsmodelsisteme te ontrafel.

\textit{Metodes} – Die muis GT1-7 neuronale sellyn, afkomstig van die hipotalamus, en die muis neuroblastoom (N2a) sellyn, wat die Sweedse dubbele mutasie AVP695 (Swe) wat met AS patologie verband hou stabiel uitdruk, is gebruik. GT1-7 selle wat met mRFP-GFP-LC3 en GFP-LC3-RFP-LC3$\Delta$G getransfekteer is, is behandel met 'n lae en ho{\"e} konsentrasie spermidien en rilmenidien in die afwesigheid en teenwoordigheid van versadigde konsentrasies bafilomisien, waarna die outofagiese stroomprofiel gekarakteriseer was deur die evaluering van sellulêre lewensvatbaarheid, outofagosoom poel, outolisosoom poel, outofagosoom stroom, oorgangstyd, p62 stippels en outofagiese vakuole. Sellul{\^e}re lewensvatbaarheidstoetse, westelike klad, fluoressensiemikroskopie, transmissie-elektronmikroskopie en korrelatiewe lig- en elektronmikroskopie (KLEM) gekoppel aan kwantitatiewe morfometriese analise is uitgevoer. Die moontlikke beskermende effekte van 'n lae en ho{\"e} konsentrasie spermidien en rilmenidien is ook beoordeel in 'n paraquat- (PQ) ge{\"i}nduseerde neuronale toksisiteitsmodel en in 'n AVP-ooruitdrukking model. Sellul{\^e}re lewensvatbaarheid, RSS-skade, aanvang van seldood en outofagiese aktiwiteit is beoordeel in die PQ-ge{\"i}nduseerde toksisiteitsmodel, terwyl sellul{\^e}re lewensvatbaarheid en prote{\"i}entrosse in die AVP-model beoordeel en gekwantifiseer is met behulp van sellul{\^e}re lewensvatbaarheidstoetse en enkelmolekule-beelding, d.w.s. d-STORM. Verder is ‘n KLEM-metode ge{\"o}ntwikkel en ge{\"i}mplementeer om die gevolge van 'n lae en ho{\"e} konsentrasie spermidien op die lokalisering van outofagosome in drie dimensies morfometries te beoordeel. Laastens is die moontlikke beskermende effekte van spermidien met twee verskillende konsentrasies beoordeel met behulp van transgeniese muise wat GFP-LC3 uitdruk en behandel is met PQ om neuronale toksisiteit wat verband hou met neurodegenerasie te induseer.

\textit{Resultate} - Ons resultate dui op 'n konsentrasie-afhanklike effek van spermidien en rilmenidien op outofagiese stroom waar die waargenome verandering in stroom afhanklik is van die spesifisiteit en sensitiwiteit van die metode wat toegepas word. Boonop het ons resultate in die \textit{in vitro} model van PQ-ge{\"i}nduseerde toksisiteit aan die lig gebring dat spermidien teen 'n lae konsentrasie maar nie teen 'n ho{\"e} konsentrasie beskermend is teen seltoksisiteit, RSS-skade, seldood en mikrotubulie-destabilisasie. Tot ons verbasing kon beide konsentrasies rilmenidien nie teen RSS-skade en seldood beskerm nie, en het ook nie daarin geslaag om outofagie in dieselfde model te opreguleer nie. Verder, in die \textit{in vitro} model van neuronale toksisiteit wat deur AVP-ooruitdrukking veroorsaak word, het ons resultate getoon dat beide konsentrasies spermidien en rilmenidien beskermend is teen sitotoksisiteit. Hier het ‘n lae konsentrasie spermidien effektief AVP-trosse skoongemaak en hul grootte verminder, veral na 48 uur van AVP-ooruitdrukking, terwyl rilmenidien die aantal en grootte van die AVP-trosse op 'n konsentrasie-afhanklike manier op dieselfde tydstip verminder het. Saamgevat toon die in vitro resultate 'n konsentrasie-afhanklike effek, wat ook afhanklik is van seltipe en besering, wat outofagie en die beheer van seldood be{\"i}nvloed. Daarbenewens het ons 'n 3D KLEM-protokol suksesvol ge{\"i}mplementeer en het aan die lig gebring dat spermidien, in kombinasie met BafA1, die volume van die outofagosoom verlaag terwyl die oppervlakte op 'n konsentrasie-afhanklike manier vergroot. Laastens, \textit{in vivo} toon ons resultate dat PQ-ge{\"i}nduseerde toksisiteit die breinstreke tot verskillende mates be{\"i}nvloed, met die hippokampus wat die mees vatbaarste is vir PQ-ge{\"i}nduseerde skade gevolg deur die korteks. Daarbenewens toon ons resultate dat beide dosisse spermidien kragtige beskerming gebied het teen oksidatiewe stress, neuronale skade en mikrotubulie-destabilisasie en het outofagie opgereguleer in die hippokampus en korteks. Die lae dosis spermidien het egter meer beskerming gebied, alhoewel outofagie in ‘n streek- en dosis-afhanklike manier opgereguleer was, met die ho{\"e}r dosis spermidien wat LC3-II in die hippokampus verhoog en die laer dosis wat LC3-II in die korteks verhoog.

\textit{Gevolgtrekking} - Ons resultate dui op die kritiese belang van die gebruik van veelvuldige metodes om outofagie te evalueer en toon dat daar 'n konsentrasie-afhanklike effek van die twee geselekteerde middels op outofagiese stroom is. Daarbenewens lewer ons bewyse vir die eiesoortige, konteks-afhanklike beskermende rol van spermidien en rilmenidien in 'n \textit{in vitro} model van AVP-ooruitdrukking, sowel as die beskermende rol van spermidien in \textit{in vitro} en \textit{in vivo} modelle van PQ-ge{\"i}nduseerde neuronale toksisiteit. Hierdie resultate dui daarop dat eerstens, die toediening van spermidien 'n gunstige terapeutiese strategie vir die behandeling van AS verteenwoordig en tweedens, dat konsentrasie / stroomsifting belangriker is vir optimale behering van outofagie as wat voorheen gedink was. Toekomstige studies, met behulp van 'n \textit{in vivo} model van AVP-ooruitdrukking, word benodig om die beskermende effekte van spermidien verder te bevestig om sodoende kliniese vertaling en terapeutiese ingryping in neurodegeneratiewe versteurings te ondersteun.

%-------------------------------------------------------------------------------
% Acknowledgements
%-------------------------------------------------------------------------------
\chapter{Acknowledgements}

\noindent
I would like to express my sincere gratitude to the following people for their help and support, without whom this dissertation would not
have been possible. \\

\noindent
My supervisor, Prof Ben Loos, thank you so much for always believing in me even at times when I doubted myself. I will be forever grateful to you for all of the opportunities you have provided me with and for guiding me to become a better researcher. I cannot imagine having gone through my PhD studies without you as my supervisor and mentor. It has been an immense honour to be one of your students. \\

\noindent
My co-supervisor, Prof Craig Kinnear, thank you so much for your assistance with all plasmid expansion related work. Without your help, this dissertatoin would not have been possible.\\

\noindent
I would also like to thank the staff and students in the Department of Physiological Sciences. A special thank you goes to the NRG group members for your friendship, critical discussions, and your willingness to lend a helping hand. To Andr{\'e} du Toit, thank you for everything you have assisted me with and thank you for your friendship. Words cannot express my gratitude. To Jurgen, thank you for all your help, you are the best. To Leah and Nicola, thank you for trusting me to co-supervise your Honours project; it definitely was a valuable experience during my PhD journey. To Bali, Theo and Danzil, thank you for the help as well as the typical Friday afternoon relaxation and chats at the Happy Oak. Lastly, also thank you to all the other staff members in the Department of Physiological Sciences, including Judy, Grazelda, Jonnifer, Annadie. \\

\noindent
Thank you to Lize Engelbrecht, Lydia Joubert, and Madelaine Frazenburg at the Central Analytical Facility (CAF) for all your assistance, particularly with the sectioning and imaging of the correlative work. We made a great team. Thank you to Reggie Williams for assisting with the brain tissue sections, and Noel Markgraff for the assistance with the GFP-LC3 mice. \\

\noindent
Thank you to Dr Lucy Collinson for giving me an opportunity to visit her at The Francis Crick in London. To Matt Russell, Christopher Peddie, and Marie-Charlotte Domart: thank you for sharing your knowledge on Correlative Light and Electron Microscopy with me. More importantly, thank you to all of you for the beautiful FIB-SEM images and for being the best collaborators. The CLEM work would not have been possible without your guidance and your willingness to help. \\

\noindent
Thank you to the postgraduate and international office at Stellenbosch University and University of T{\"u}bingen for granting me the opportunity to go for an extended laboratory visit in Germany. To Prof Tassula Proikas-Cezanne; thank you for opening your lab and for welcoming me as one of your group members.\\

\noindent
To Madelaine, thank you for being more than a colleague to me. Thank you for all your support and thank you for pushing me to finish. Most importantly, thank you for your friendship and guidance. You simply are the best.\\

\noindent
To Rozanne, I honestly cannot express how thankful I am for having you as a friend, a colleague, and partner throughout my PhD journey. Thank you for allowing me to drag you into my night shifts in the lab running western blots. You have made this work-PhD life balance a whole lot easier to handle and I could not have wished for anyone else to walk through this journey with me.\\

\noindent
To my sisters from another mother, Zandile, Nwabisa and Celi, thank you for being there when I needed a shoulder to cry on. Thank for your endless support. Thank you for going through the PhD journey before I did, your advice have been tremendously helpful and I could not have done it without you. And most importantly, thank you for your friendship.\\

\noindent
To my sisters Zodumo and Tulani, my brother Sango, and my in-laws, Annemieke, Rik, Sean, Sarah and Lenore, thank you for all your endless support.\\

\noindent
To my kids Sihle, Amzolele, Amvelo and Yolatha, thank you for being the bundle of  joy in my life. I love you.\\

\noindent
Ku Tata uMvulane no mama uMamncotshe, enkosi ngenxaso enindinikeze yona, amagama akanokuze acacise umbulelo endinawo kuni. Enkosi ngondithanda. Enkosi ngenxaso yenu. Ekubalulekileyo ngaphezu kwazo zonke, enkosi ngokuncama yonke into kuba ninomqweno wokufezekisa amaphupha am. Bendingenoze ndiwafezekise amaphupha am ngaphandle kwenxaso yenu. This one is for you guys.\\

\noindent
And lastly, to my husband, Dr Justin van Dijk, who keeps insisting that I call him Dr, thank you for sharing my ambitions. Thank you for believing in me. Thank you for pushing me to be the best that I can be. Thank you for handling all the cooking. And most importantly, thank you for your love and support. Ik houd van je.

%-------------------------------------------------------------------------------
% Output
%-------------------------------------------------------------------------------
\chapter{Publications and conference presentations}

\subsection*{Refereed publications and book chapters}
\begin{enumerate}
\item \textbf{Lumkwana, D.}, Du Toit, A., Kinnear, C. \& Loos, B., 2017. Autophagic flux control in neurodegeneration: Progress and precision targeting — Where do we stand? \textit{Progress in Neurobiology} 153: 65-85.
\item Ntsapi, C., \textbf{Lumkwana, D.}, Swart, C., Du Toit, A. \& Loos, B., 2017. New insights into autophagy dysfunction related to amyloid beta toxicity and neuropathology in Alzheimer’s Disease. In: International Review of Cell and Molecular Biology, Volume 336. London: Elsevier, pp. 321-361.
\item Ntsapi, C., Swart, C., \textbf{Lumkwana, D.} \& Loos, B., 2016. Autophagic flux failure in neurodegeneration: Identifying the defect and compensating flux offset. In: Gorbunov N.V. \& Schneider, M. (eds.). Autophagy in current trends in cellular physiology and pathology. London: InTech Open, pp. 157-176.
\end{enumerate}

\subsection*{Presentations at international conferences}
\begin{enumerate}
\item Poster presented at the Focus On Microscopy (FOM) conference. \textit{Assessment of amyloid precursor protein (APP) and tubulin network using stochastic optical reconstruction microscopy (STORM) in an in vitro model of Alzheimer's disease.} April 2019. London, United Kingdom.
\item Paper presented at the Microscopy Society of Southern Africa (MMSA). \textit{Investigating the role of Rilmenidine and Spermidine in an in vitro model of Alzheimer's disease.} December 2016. Port Elizabeth, South Africa.
\item Poster presented at Physiology Society of Southern Africa (PSSA). \textit{The role of Rilmenidine and Spermidine in autophagic flux and cell death in a model of paraquat-induced neuronal toxicity.} September 2016. Cape Town, South Africa.
\end{enumerate}

\subsection*{Laboratory visits}
\begin{enumerate}
\item Electron Microscopy laboratory, \textit{The Francis Crick Institute.} January 2018. \mbox{London}, United Kingdom.
\item Department of Molecular Biology (Autophagy lab), \textit{University of T{\"u}bingen.} March - August 2018. T{\"u}bingen, Germany.
\end{enumerate}
\newpage

%-------------------------------------------------------------------------------
% Table and Lists of Content
%-------------------------------------------------------------------------------
\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{4}

\tableofcontents
\newpage

\listoffigures
\newpage

\listoftables
\newpage

\chapter*{Nomenclature}
\addcontentsline{toc}{chapter}{Nomenclature}
\subsection*{Abbreviations}
\begin{itemize}[leftmargin=*,wide=0pt,]
\DTLforeach*{acronyms}{\thisAcronym=Acronym,\thisDesc=Description}
   {\item[] \textbf{\thisAcronym} \thisDesc}
\end{itemize}

\subsection*{Units of Measurements}
\begin{itemize}[leftmargin=*,wide=0pt,]
\DTLforeach*{units}{\thisUnit=Unit,\thisDesc=Description}
   {\item[] \textbf{\thisUnit} \thisDesc}
\end{itemize}
