\chapter{The effect of spermidine on PQ induced brain injury model of Alzheimer’s disease}
\section{Introduction}
In order to assess the role of autophagy enhancement in an \textit{in vivo} scenario, a PQ induced neuronal injury model was employed \citep{Chen2012}, using a GFP-LC3 transgenic mice \citep{Mizushima2004a}. Specifically, since the concentration dependent effect of autophagy induction was of major interest, this part of the work was focussing on spermidine at two distinct concentrations. In this context, we focused primarily on the brain regions that are highly susceptibility to neuronal injury as we previously reviewed in detail \citep{lumkwana2017}. These regions include the hippocampus and the cortex which are impacted in early and late stages of AD respectively and have been shown to have manifest with major pathological changes, including cell loss. So far, the role of spermidine in a mouse model of PQ-induced injury has not been assessed. Therefore, the aims of this chapter were to assess the extent of PQ induced toxicity in terms lipid peroxidation and to assess the role of spermidine in protein clearance, tubulin acetylation and subsequent potential protection. A total of 72 mice expressing GFP-LC3 were randomly selected into 6 groups of 12 consisting of (1) control (saline solution), (2) PQ, (3) 0.3 mM Spd, (4) 0.3 mM Spd + PQ, (5) 3 mM Spd and (6) 3 mM Spd + PQ. The study was conducted for 21 days in which saline and PQ was administered every 3 days for 21 days \citep{Chen2012}, with a total of 6 injections, while other animals had ad libitum access to spermidine in the drinking water for the duration of the treatment. After 21 days, animals were sacrificed and brain was extracted, weighted and dissected into different regions, namely hippocampus and cortex and prepared accordingly for H\&E, western blotting, and immunofluorescence. Markers of oxidative stress (4HNE), autophagy (LC3 II, p62, LAMP2a), brain injury [glial fibrillary acidic protein (GFAP) and amyloid precursor protein (APP)] and microtubule stability (acetylated $\alpha$-tubulin) were assessed. 

\section{Effect of treatment intervention on brain weight}
In order to assess the effect of the treatment intervention on brain weight, cerebral tissue was weighed immediately after animal sacrifice and brain extraction. Results show a significant increase in the brain weight in the PQ treated group (1.08 $\pm$ 0.02, \textit{p} < 0.05), 0.3 mM Spd (1.21 $\pm$ 0.04, \textit{p} < 0.05), 0.3 mM Spd + PQ (1.20 $\pm$ 0.01, p < 0.05), 3 mM Spd (1.16 $\pm$ 0.01, \textit{p} < 0.05) and 3 mM Spd + PQ (1.19 $\pm$ 0.04, \textit{p} < 0.05) compared to the control group (1.00 $\pm$ 0.01) (Fig.7.1). In addition, a significant increase in brain weight was also observed in the 0.3mM Spd, 0.3mM Spd + PQ, 3mM Spd and 3mM Spd + PQ compared to the PQ treated group. 

%figure
%figure references

\section{Effect of treatment intervention on hippocampus and cortex}
The hippocampus and cortex are regions susceptible to pathological changes particularly in PD (Braak et al., 2004, 2003, 1998), but also in AD (Braak et al., 2000, 1998; Braak and Braak, 1991; Braak and Del Tredici, 2012). Therefore, the effect of the treatment intervention in a PQ-induced brain injury model was assessed using Heamatoxylin and Eosin (H\&E), western blotting and immunofluorescence. Protein expression levels indicative of oxidative stress (4HNE), brain injury (GFAP and APP), autophagy activity (LC3 II, p62, and LAMP2A), and microtubule stability (acetylated $\alpha$-tubulin) were assessed in both brain regions and complemented with immunofluorescence.

%add bibliographical references (Braak)

\section{Hippocampus region}
\subsection{Heamatoxylin and Eosin (H\&E) staining}
In order to assess overall structural changes of the hippocampus following treatment intervention, H\&E staining was carried out. No major abnormalities or neuronal cell loss were observed between the treatment groups (Fig.7.2). No signs for architectural damage or protein inclusion were observed.

%figure
%figure references

\subsection{Lipid peroxidation (4HNE) assessment using western blotting}
The lipid peroxidation end product 4-hydroxy-2-nonenal (4HNE), a marker for oxidative stress was assessed in response to treatment intervention. Three distinct 4HNE protein adducts bands (35, 45, 52 kDa) were identified. At 35 kDa, 4HNE signal was significantly increased in the PQ treated group (1.84 $\pm$ 0.18, \textit{p} < 0.05), while significantly decreased in the 0.3 mM Spd (0.29 $\pm$ 0.04, \textit{p} < 0.05), 0.3 mM Spd + PQ (0.39 $\pm$ 0.08, \textit{p} < 0.05), 3 mM Spd (0.36 $\pm$ 0.09, \textit{p} < 0.05) and 3 mM Spd + PQ (0.57 $\pm$ 0.09, \textit{p} < 0.05) compared to the control group (0.88 $\pm$ 0.10) (Fig.7.3.A.i). Moreover, a significant decrease in 4HNE signal was also observed with 0.3 mM Spd, 0.3 mM Spd + PQ, 3 mM Spd and 3mM Spd + PQ (\textit{p} < 0.05) compared to the PQ treated group. 

Similarly at 45 kDa, 4HNE signal was significantly increased in the PQ treated group (1.41 $\pm$ 0.22, \textit{p} < 0.05), while significantly decreased in the 0.3 mM Spd + PQ (0.13 $\pm$ 0.03, \textit{p} < 0.05), 3 mM Spd (0.32 $\pm$ 0.05) and 3 mM Spd + PQ (0.23 $\pm$ 0.05) compared to the control (0.95 $\pm$ 0.13) (Fig.7.3.A.ii). Additionally, in comparison to the PQ treated group, a significant decrease in 4HNE expression was also observed in the 0.3 mM Spd, 0.3 mM Spd + PQ, 3 mM Spd and 3 mM Spd + PQ. Furthermore, a significant decrease was observed in the 0.3 mM Spd + PQ and 3 mM Spd (\textit{p} < 0.05) compared to 0.3 mM Spd.

Lastly at 53 kDa , no significant differences were observed in 4HNE signal in the PQ treated group (1.42 $\pm$ 0.34), 0.3 mM Spd (1.48 $\pm$ 0.22) and in 3 mM Spd (0.76 $\pm$ 0.22) compared to the control (1.00 $\pm$ 0.12), however, a significant decrease in 4HNE signal was detected in the 0.3 mM Spd + PQ (0.46 $\pm$ 0.15) and 3 mM Spd + PQ (0.45 $\pm$ 0.07) group (Fig.7.3.A.iii). In comparison to the PQ treated group, a significant decrease in 4HNE signal was revealed in the 0.3 mM Spd + PQ, 3 mM Spd and 3 mM Spd + PQ. Furthermore, a significant decrease was observed in the 0.3 mM Spd + PQ (\textit{p} < 0.05) compared to 0.3 mM Spd and in 3 mM Spd (\textit{p} < 0.05) compared to 0.3 mM Spd. 

%figure
%figure references

\subsection{4HNE assessment using fluorescence microscopy}
4HNE fluorescence intensity was assessed following treatment intervention using a confocal microscopy. Results show a strong fluorescence intensity signal in the PQ treated group to all other groups; control, 0.3mM Spd, 0.3mM Spd + PQ, 3mM Spd and 3mM Spd + PQ (Fig.7.4).

%figure
%figure references

\subsection{GFAP assessment using fluorescence microscopy} 
Glial fibrillary protein (GFAP) and its upregulation has been utilized as a marker for neuronal damage (Wu et al., 2015). Here, we assessed the role of spermidine in impacting GFAP upon PQ-induced damage. A strong fluorescence intensity signal for GFAP was observed in the PQ treated group with distinct glial derived signal compared to all other groups (Fig.7.5)

%add bibliographical references (Wu2015)
%figure
%figure references

\subsection{APP assessment using western blotting}
Next, APP expression which has been used as an indicator of neuronal damage was assessed following treatments using western blot analysis. Our results reveal that APP expression was significantly increased following treatment with PQ (2.60 $\pm$ 0.17) and 0.3 mM Spd (2.21 $\pm$ 0.13) compared to the control group (1.00 $\pm$ 0.57) (Fig.7.6). Of particular importance is a significant decrease in APP expression with 0.3 mM Spd + PQ (\textit{p} < 0.05), 3 mM Spd (\textit{p} < 0.05) and 3 mM Spd + PQ (\textit{p} < 0.05) compared to the PQ treated group. Furthermore, a significant decrease in APP expression was observed in the 0.3 mM Spd + PQ (\textit{p} < 0.05) and 3 mM Spd (\textit{p} < 0.05) compared to 0.3 mM Spd. 

%figure
%figure references

\subsection{Acetylated $\alpha$-tubulin assessment using western blotting}
In order to assess whether autophagy upregulation through spermidine may impact microtubule stability, acetylated $\alpha$-tubulin was assessed in response to treatment intervention. In comparison to the control group (1.00 $\pm$ 0.08), a significant decrease in tubulin acetylation was observed in the PQ treated group (0.68 $\pm$ 0.05, \textit{p} < 0.05) (Fig.7.7). Moreover, a significant increase in acetylated $\alpha$-tubulin was observed in the 0.3 mM Spd + PQ (1.11 $\pm$ 0.04, \textit{p} < 0.05), and 3 mM Spd + PQ (0.99 $\pm$ 0.13, \textit{p} < 0.05) compared to the PQ treated group (0.68 $\pm$ 0.05). Furthermore, a significant increase was observed in 0.3 mM Spd + PQ (1.11 $\pm$ 0.04, \textit{p} < 0.05) compared to 0.3 mM Spd (0.82 $\pm$ 0.05).

%figure
%figure references

\subsection{Autophagy activity assessment using western blotting}
In order to assess autophagic activity in response to treatment intervention in the hippocampus, LC3 II, p62 and LAMP2A protein levels were assessed using western blot and fluorescence microscopy. Results indicate that LC3 II protein expression was significantly increased in the 0.3 mM Spd + PQ (1.38 $\pm$ 0.11, \textit{p} < 0.05) and the 3 mM Spd + PQ (1.67 $\pm$ 0.12, \textit{p} < 0.05) compared to the control group (1.00 $\pm$ 0.06) and PQ treated group (0.91 $\pm$ 0.06) (Fig.7.8.A.i). Moreover, LC3 II protein levels were significantly increased in the 3 mM Spd + PQ (\textit{p} < 0.05) compared to the 0.3 mM Spd + PQ, with no significant difference observed between 0.3 mM Spd (1.17 $\pm$ 0.05) and 3 mM Spd (1.13 $\pm$ 0.08). Lastly, LC3 II expression was significantly increased in the 3 mM Spd + PQ compared to the 3 mM Spd, \textit{p} < 0.05.

In comparison to the control group (1.00 $\pm$ 0.07) and PQ treated group (0.71 $\pm$ 0.07), a significant increase in the p62 protein expression was observed in the 3 mM Spd (2.60 $\pm$ 0.72, \textit{p} < 0.05) and in 3 mM Spd + PQ (2.59 $\pm$ 0.45, \textit{p} < 0.05) (Fig.7.8.A.ii). In addition, 3 mM Spd exposure significantly increased p62 protein expression compared to 0.3 mM Spd (2.60 $\pm$ 0.72 vs 0.76 $\pm$ 0.29).

LAMP2A protein expression was significantly decreased in the PQ treated group (0.09 $\pm$ 0.02, \textit{p} < 0.05), while significantly increased in 0.3 mM Spd (2.43 $\pm$ 0.27, \textit{p} < 0.05), 0.3 mM Spd + PQ (1.92 $\pm$ 0.22, \textit{p} < 0.05) and 3 mM Spd + PQ (1.90 $\pm$ 0.35, \textit{p} < 0.05) compared to the control group (1.00 $\pm$ 0.33) (Fig.7.8.A.iii). Moreover, LAMP2A protein expression was significantly increased in 0.3 mM Spd (2.43 $\pm$ 0.27), 0.3 mM Spd + PQ (1.92 $\pm$ 0.22), 3 mM Spd (1.80 $\pm$ 0.32) and 3 mM Spd + PQ (1.90 $\pm$ 0.35) compared to the PQ treated group (0.09 $\pm$ 0.02).

%figure
%figure references

\subsection{GFP-LC3 assessment using fluorescence microscopy}
Results show that GFP-LC3 fluorescence intensity signal was strongly expressed in the groups where spermidine was present i.e. in the 0.3 mM Spd, 0.3 mM Spd + PQ, 3 mM Spd, and 3 mM Spd + PQ as well as in the control group compared to the PQ treated group (Fig 7.9).

%figure
%figure references

\subsection{p62 assessment using fluorescence microscopy}
A strong fluorescence intensity signal for p62 was observed in the 3 mM Spd and 3 mM Spd + PQ compared to PQ treated group and control group as shown in Fig.7.10.

%figure
%figure references

\section{Cortex region}
\subsection{Heamatoxylin and Eosin (H\&E) staining}
Qualitative analysis using H\&E staining showed no major abnormal changes in the structural architecture of the cortex upon treatment intervention (Fig.7.11).

%figure
%figure references

\subsection{Lipid peroxidation (4HNE) assessment using western blotting}
At 35 kDa, 4HNE protein adducts signal was significantly decreased in the 0.3 mM Spd (0.59 $\pm$ 0.09, \textit{p} < 0.05), 0.3 mM Spd + PQ group (0.47 $\pm$ 0.08, \textit{p} < 0.05) compared to the control group (1.00 $\pm$ 0.14) with no significant increase observed in the PQ treated group (1.08 $\pm$ 0.17) (Fig.7.12.A.i). Moreover, 4HNE signal was significantly decreased in the 0.3 mM Spd (\textit{p} < 0.05) and 0.3 mM Spd + PQ group (\textit{p} < 0.05) compared to the PQ treated group. 

At 45 kDa, 4HNE signal was significantly decreased in the 0.3 mM Spd (0.45 $\pm$ 0.06, \textit{p} < 0.05), 0.3 mM Spd + PQ (0.14 $\pm$ 0.05, \textit{p} < 0.05), 3 mM Spd (0.26 $\pm$ 0.04) and 3 mM Spd + PQ (0.18 $\pm$ 0.04, \textit{p} < 0.05) compared to the control (1.00 $\pm$ 0.08) and PQ treated group (1.05 $\pm$ 0.130), with no significant differences seen between the control and the PQ treated group (Fig.7.12.A.ii). Moreover, a significant decrease was observed in 0.3 mM Spd + PQ compared to 0.3 mM Spd (\textit{p} < 0.05) and in 3 mM Spd (\textit{p} < 0.05) compared to 0.3mM Spd, 
Lastly, at 52 kDa, a significant decrease in 4HNE signal was observed in the 0.3 mM Spd + PQ (0.14 $\pm$ 0.05, \textit{p} < 0.05), 3 mM Spd (0.15 $\pm$ 0.07) and 3 mM Spd + PQ (0.11 $\pm$ 0.05, \textit{p} < 0.05) group compared to the control (1.00 $\pm$ 0.22) and PQ treated group (0.99 $\pm$ 0.17) (Fig.7.12.A.iii). Moreover, 4HNE expression of was significantly decreased in the 0.3mM Spd + PQ (0.14 $\pm$ 0.05) and in the 3 mM Spd (0.15 $\pm$ 0.07) compared to 0.3mM Spd (0.62 $\pm$ 0.13).

%figure
%figure references

\subsection{4HNE signal assessment using fluorescence microscopy}
A moderately enhanced fluorescence signal for 4HNE was observed in the control and PQ treated group compared to 0.3mM Spd, 0.3mM Spd + PQ, 3mM Spd and 3mM Spd + PQ (Fig.7.13).

%figure
%figure references

\subsection{GFAP assessment using fluorescence microscopy}
Results indicate that GFAP fluorescence intensity signal was strongly enhanced in the PQ treated group compared to all other groups (Fig.7.14).

%figure
%figure references

\subsection{APP assessment using western blotting}
Although no significance differences was reached, a trend towards an increase in APP was observed following PQ treatment (1.57 $\pm$ 0.36), while a trend towards decreased APP signal was observed following treatment with 0.3 mM Spd (1.10 $\pm$ 0.22), 0.3 mM Spd + PQ (0.65 $\pm$ 0.19), 3 mM Spd (1.17 $\pm$ 0.25) and 3 mM Spd + PQ (0.70 $\pm$ 0.23) compared to the control group (0.58 $\pm$ 0.16) (Fig.7.15). Of particular importance is a significant decrease in APP expression with 0.3 mM Spd + PQ (\textit{p} < 0.05) and 3 mM Spd + PQ (\textit{p} < 0.05) compared to the PQ treated group. 

%figure
%figure references

\subsection{Acetylated $\alpha$-tubulin assessment using western blotting}
In comparison to the control (1.00 $\pm$ 0.03) and PQ treated group (0.87 $\pm$ 0.13), no significant differences were observed in the expression of acetylated $\alpha$-tubulin in the 0.3 mM Spd (0.95 $\pm$ 0.17), 0.3 mM Spd + PQ (0.80 $\pm$ 0.08) and 3 mM Spd (1.02 $\pm$ 0.07), however, a significant decrease was observed at 3 mM Spd + PQ (0.65 $\pm$ 0.12, \textit{p} < 0.05) compared to the control and PQ group (Fig.7.16). 

%figure
%figure references

\subsection{Autophagy activity assessment using western blotting}
No significant differences in LC3 II protein levels were observed in the PQ treated group (0.65 $\pm$ 0.03) compared to the control group (1.00 $\pm$ 0.11) (Fig.7.17.A.i). A significant increase in LC3 II expression was however observed in the 0.3 mM Spd + PQ (1.30 $\pm$ 0.27, \textit{p} < 0.05) and 3 mM Spd (1.23 $\pm$ 0.25, \textit{p} < 0.05) compared to the PQ treated group (0.65 $\pm$ 0.03). 

No significant differences were observed in the p62 expression following treatment with PQ (1.15 $\pm$ 0.11), 3 mM Spd (1.66 $\pm$ 0.21) and 3 mM Spd + PQ (1.56 $\pm$ 0.34) compared to the control  group (1.00 $\pm$ 0.06), however, a significant increase in p62 expression was observed in the 0.3 mM Spd (2.53 $\pm$ 0.34) and 0.3 mM Spd + PQ (2.43 $\pm$ 0.36, \textit{p} < 0.05) (Fig.7.17.A.ii). Moreover, a significant increase was also detected in the 0.3 mM Spd and 0.3 mM Spd + PQ group compared to PQ treated group. More importantly, a significant decrease in p62 expression was observed in the combination treatment (3mM Spd + PQ) compared to 0.3mM Spd + PQ as well as in the 3 mM Spd treated group compared to 0.3mM Spd. 

No significant differences were observed in LAMP2A protein expression in the PQ treated group (0.40 $\pm$ 0.13) compared to the control group (1.00 $\pm$ 0.18), however a significant increase in LAMP2A expression was observed with 0.3 mM Spd + PQ (2.02 $\pm$ 0.39, \textit{p} < 0.05) and 3 mM Spd (2.16 $\pm$ 0.53, \textit{p} < 0.05) compared to the control group (Fig.7.17.A.iii). Moreover, LAMP2A expression was significantly increased in 0.3mM Spd (1.85 $\pm$ 0.24), 0.3 mM Spd + PQ (2.02 $\pm$ 0.39), 3 mM Spd (2.16 $\pm$ 0.53) and 3mM Spd + PQ (1.47 $\pm$ 0.14) compared to the PQ treated group (0.40 $\pm$ 0.13).

%figure
%figure references

\subsection{GFP-LC3 assessment using fluorescence microscopy}
Fluorescence microscopy of the cortex showed that GFP-LC3 signal was enhanced in the groups 0.3 mM Spd + PQ and 3mM Spd (Fig.7.18).

%figure
%figure references

\subsection{p62 assessment using fluorescence microscopy}
A strong fluorescence intensity signal for p62 was observed in the PQ treated group compared to all other groups; 0. 3 mM Spd and 0.3 mM Spd + PQ (Fig.7.19).

%figure
%figure references

\section{Discussion: The effect of spermidine on a PQ-induced brain injury model of Alzheimer's Disease}
Mounting evidence point towards autophagy modulation using pharmacological agents as one of the major therapeutic strategies for neurodegenerative diseases \citep{Hebron2013,Jiang2014a,Perera2018,Ravikumar2004,Rose2010}. In particular, spermidine, a natural polyamine, has been shown to ameliorate neurodegeneration associated pathologies in mouse models of ischemia \citep{Morrison2002}, normal tension glaucoma \citep{Noro2015}, ALS \citep{Wang2012} and  PD \citep{Buttner2014} and recently in mouse and human models of ageing \citep{Schwarz2018,Wirth2019,Wirth2018}. Moreover, as a CRM, spermidine is known to enhance longevity by enhancing autophagy \citep{Marino2014}. Whether the protective effects of spermidine are concentration dependent remains unclear. Moreover, spermidine has not been assessed in AD models. Hence, the purpose of this study was to assess the protective effects of spermidine at two distinct concentrations using transgenic mice expressing GFP-LC3 \citep{Mizushima2004a} that were treated with PQ to induce neuronal toxicity associated with neurodegeneration \citep{Chen2012}. PQ is a pesticide that selectively targets neurons in the substantia nigra (SN) pars compacta leading to PD like neuropathology i.e. degeneration of nigral dopaminergic neurons \citep{McCormack2005, McCormack2002}. Although PQ preferentially affects SN pars compacta, it can accumulate in the hippocampus and cortex \citep{Landrigan2005}, thus, it could potentially impair learning and memory functions and affect AD pathogenesis. PQ exact its toxicity by inducing oxidative stress and mitochondrial damage \citep{Baltazar2014,Drechsel2008, Lin2006}, both of which are implicated in the pathogenesis of AD \citep{Lin2006}. Hence, here we focussed on the hippocampus and the cortex, the two brain regions important for cognition, and most susceptible to neuronal injury, impacted in the early and late stages of AD respectively.

\section{Effect of treatment intervention on brain weight}
We first assessed the effects of PQ and spermidine on brain weight. After 21 days of treatment intervention, our results revealed a significant increase in brain weight in PQ treated group, spermidine treatment alone at both concentrations (0.3 mM \& 3 mM Spd) and in combination treatment with PQ at both concentrations (0.3 mM Spd + PQ \& 3 mM Spd + PQ) compared to the control group (Fig.7.1). Moreover, a significant increase in brain weight was observed following treatment, alone and in combination group compared to the PQ treated group. The increase in brain weight following PQ treatment might be due to osmotic swelling. PQ has been proposed to induce to induce mitochondrial toxicity by inducing osmotic swelling \citep{Cappelletti1996,Mohammadi-Bardbori2008}. However, since spermidine alone and in combination with PQ increased brain weight above the weight observed in the PQ group alone, these results suggest that the increased brain weight might be due to enhanced synaptic plasticity, which plays a role in promoting memory formation. Indeed, previous work showed that spermidine protects against age induced memory impairment in fruitflies \citep{Gupta2016,Gupta2013,Sigrist2014}. And more recent work demonstrate that spermidine works directly at the synapses where it regulates presynaptic specialization in an autophagy dependent mechanism \citep{Bhukel2017}. Since all tissues have basal autophagy, and that stress upregulates autophagy, and that PQ is a neurotoxin, the increase in brain weight in the PQ group might have been due to enhanced synaptic plasticity caused upregulation of autophagy. This warrants further investigation.
%cross ref fig7.1

\section{Hippocampus region analysis} 
\subsection{The effect of treatment intervention on H\&E staining}
In order to assess overall structural changes of the hippocampus following treatment intervention, H \& E staining was performed. Our data revealed no major abnormalities i.e. no signs of neuronal cell loss and architectural damage or protein inclusion between the treatment groups (Fig.7.2). These results suggest that PQ-induced toxicity in the brain was not severe to cause structural damage in this region. Indeed, silver staining of brain sections PD models revealed degeneration neurons in the SN pars compacta in mice exposed to PQ once a week for 3 weeks \citep{McCormack2002}. Other studies reported in the same brain region that PQ exposure enhanced $\alpha$-synuclein aggregation \citep{Manning-Bog2002} and induced neuronal injury \citep{Manning-Bog2003}.
%cross ref fig 7.2
\subsection{The effect of treatment intervention on lipid peroxidation}
Because PQ induces oxidative stress, we assessed 4HNE adducts at 35, 45, 52 kDa. Our results at 35 kDa revealed a significant increase in 4HNE signal following PQ treatment and a significant reduction in 4HNE signal following treatment with spermidine (0.3 mM Spd, 0.3 mM Spd + PQ, 3 mM Spd, and 3 mM Spd + PQ) compared to the control group (Fig.7.3.A.i). Secondly, a significant decrease in 4HNE signal following spermidine treatment compared to the PQ treated group. At 45 kDa, our results showed a significantly enhanced 4HNE signal following PQ treatment and a significant reduction in 4HNE signal following spermidine treatment compared to the control group, with the exception of 0.3 mM Spd (Fig.7.3.A.ii). Secondly, results show a significant reduction in 4HNE signal following treatment with spermidine compared to the PQ treated group. Thirdly, we observed a significant reduction in 4HNE signal in the 0.3 mM Spd + PQ compared to 0.3 mM Spd and in 3 mM Spd compared to 0.3 mM Spd. To our surprise, at 55 kDa, we observed no significant differences in 4HNE signal in the PQ treated group, 0.3 mM Spd and in 3 mM Spd compared to the control, but, a significant reduction in 4HNE signal was detected in the combination (0.3 mM Spd + PQ and 3 mM Spd + PQ) groups (Fig.7.3.A.iii). Secondly, we revealed a significant reduction in 4HNE signal following spermidine treatment compared to the PQ treated group, with the exception of 0.3 mM Spd. Lastly, we observed a significant reduction in the 0.3 mM Spd + PQ compared to 0.3 mM Spd and in 3 mM Spd compared to 0.3 mM Spd. These results are supported by the immunofluorescence data, where a strong 4HNE signal was observed following PQ treated group compared to all other groups (Fig.7.4). In overall, these results suggest that (1) PQ exposure induces oxidative stress or damage, (2) spermidine supplementation protects against oxidative stress induced by PQ and (3) spermidine mediates neuroprotection in a concentration dependent. In line with our findings, \citet{Chen2012} revealed that PQ exposure in mice over a period of 21 days resulted in oxidative damage. Furthermore, studies \textit{in vivo} have reported that spermidine reduces oxidative damage in various diseases, in a mouse model of retinal degenerative disease \citep{Noro2015}, in \textit{Drosophila melanogaster} model of PQ induced neurotoxicity \citep{Minois2012}, mouse model of ageing \citep{Eisenberg2009} and rat model of HD \citep{Jamwal2016}. In the latter study, systematic exposure to 3 nitropropanoic acid (3NP), a compound that simulate HD like neuro-pathologies was found to elevate lipid peroxidation which was reduced by spermidine administration in a dose dependent manner \citep{Jamwal2016}. Overall, these studies together with our data support the anti-oxidant properties of spermidine as antioxidant agent. 
%cross reference fig
\subsection{The effect of spermidine treatment intervention on GFAP in a PQ-induced brain injury model}
Next, we assessed GFAP, a marker neuronal injury. A strong signal for GFAP was detected in the PQ treated group with distinct glial derived signal compared to all other groups (Fig.7.5), suggesting that PQ induces astrocyte gliosis as a sign for neuronal injury or neuronal damage in this region. More importantly, spermidine at 0.3 mM Spd + PQ, and 3 mM Spd + PQ reduced neuronal damage compared to the PQ treated group, suggesting that spermidine mediates neuroprotection. In support of our findings, previous reports have shown increased levels of GFAP in the mouse model of AD \citep{Kamphuis2014,Kamphuis2012} and in patients with AD in the CSF \citep{Colangelo2014,Fukuyama2001,Ishiki2016} and in the hippocampus \citep{Kamphuis2014}. Notably, spermidine has been shown to inhibit gliosis in a mouse model of multiple sclerosis, an inflammatory disease \citep{Guo2011}, while its precursor spermine has been shown to reduce GFAP signal in a rat model of HD \citep{Velloso2009}. Because GFAP is an indicator of inflammatory response, these studies together with our results suggest that spermidine mediates protection via its anti-inflammatory properties. However, the reduction of astrogliosis by spermidine might also be mediated by mechanisms dependent on autophagy. In support of this notion, others have reported a decrease in astrogliosis after autophagy modulation in models of neurodegeneration \citep{Castillo2013,Rodriguez-Navarro2010,Wang2012}. 
%cross ref (Fig.7.5)
\subsection{The effect of spermidine treatment intervention on APP expression upon PQ-induced brain injury}
Next, we assessed APP expression, another marker for neuronal damage. Consistent with GFAP data, our western blot data showed a similar pattern in the APP expression. APP expression was significantly increased following treatment with PQ compared to the control group (Fig.7.6). To our knowledge, our data indicate for the first time an increase in APP following PQ treatment. Previous studies have reported increased APP levels in neurons in the hippocampus following experimentally induced neuronal damage with kainate in a rat model \citep{Siman1989}. In this study, high levels of APP were associated with increased astrogliosis as both APP and GFAP co-localized in sites of damage, thus supporting our observations with GFAP. To our surprise, we found enhanced APP expression with 0.3 mM Spd compared to the control group. Importantly, we observed a significant decrease in APP expression with spermidine (0.3 mM Spd + PQ, 3 mM Spd and 3 mM Spd + PQ) compared to the PQ treated group, suggesting again that spermidine protects against neuronal damage in the APP context. Furthermore, a significant decrease in APP expression was observed in the 0.3 mM Spd + PQ compared to 0.3 mM Spd and in 3 mM Spd compared to 0.3 mM Spd, suggesting a concentration dependent protection by spermidine. To our knowledge, this is a first time a concentration dependent protection by spermidine in the context of APP has been reported. Overall, these results indicate that spermidine intervention ameliorates neuronal damage and confer protection. Protective effects of spermidine against neuronal damage have been reported in various studies. \citet{Yang2017} reported that spermidine protected against I/R induced injury in the hippocampus and cortical areas. Spermidine was found to mitigate $\alpha$-synuclein neurotoxicity in fruit flies and nematodes \citep{Buttner2014}, and to rescue motor dysfunction in mice with frontotemporal lobar degeneration \citep{Wang2012}.

\subsection{The effect of spermidine treatment intervention on APP expression upon PQ-induced brain injury}
Next, we assessed acetylated $\alpha$- tubulin expression.Tubulin acetylation is a hallmark of microtubule stabilization and unstable microtubules have been implicated in chronic neurodegenerative disease such as AD \citep{Phadwal2018}. Given the neuronal damage observed with PQ, we investigated whether PQ will decrease tubulin acetylation and whether autophagy enhancement through spermidine impact on microtubule stability. Our results revealed that PQ treated group significantly decreased acetylated $\alpha$-tubulin compared to the control group (Fig.7.7), suggesting that PQ causes destabilization of microtubule. In line with our findings, a decrease in acetylated $\alpha$- tubulin was reported in the midbrain of zebrafish treated with PQ (POULINP2019) and in the striata of mice \citep{Wills2012}. Notably, a significant increase in acetylated $\alpha$-tubulin was observed following spermidine treatment with both concentrations i.e. 0.3 mM Spd + PQ, and 3 mM Spd + PQ compared to the PQ treated group. Furthermore, a significant increase was observed in 0.3 mM Spd + PQ compared to 0.3 mM Spd. These results suggest that spermidine rescues against PQ induced destabilization of microtubule. Spermidine is known to increase the acetylation of tubulin by supressing EP300, and in turn stimulate autophagic flux in this manner \citep{Madeo2018}. Increased acetylation of microtubules facilitates the retrograde mobilization of autophagosomes from the periphery to the lysosomes localized in the cytoplasm for degradation \citep{Phadwal2018,Xie2010}. Therefore, we hypothesise that spermidine increases the acetylation of tubulin by suppressing EP300, leading to an increase autophagic flux, where toxic protein and organelles induced by PQ treatment are engulfed in the autophagosomes and are transported to the lysosomes for their degradation. These findings are novel and are the first report in which spermidine and autophagy are used together as a novel approach towards the degradation of PQ induced toxicity context in vivo. A recent study reported that spermine, a precursor for spermidine increases tubulin acetylation and facilitate the autophagy degradation of aggregate protein in an \textit{in vitro} model of Prion diseases \citep{Phadwal2018}.

Besides neuroprotective effects, mounting evidence suggest that spermidine plays a role in longevity in various model systems \citep{Eisenberg2009,Garcia-Prat2016,Minois2012,Morselli2011,Pietrocola2015} and that both the neuroprotective effects and life span expansion by spermidine are mediated through autophagy \citep{Eisenberg2009,Gupta2016,Gupta2013,Minois2012,Yue2017}. Hence, we investigated the role of autophagy in the context of PQ-induced toxicity. Expression of LC3-II, p62 and LAMP2A were assessed. Interestingly, our results revealed that LC3-II protein expression was significantly enhanced in spermidine treatment at both concentration i.e. 0.3 mM Spd + PQ and the 3 mM Spd + PQ compared to the PQ treated group and control group, but not in the PQ treated group itself compared to the control group (Fig.7.8.A.i). These results suggest that autophagy activity was enhanced above basal levels in response to spermidine treatment, while PQ exposure alone did not induce autophagy above control levels. Importantly, LC3-II protein levels were significantly increased in the highest concentration spermidine i.e. 3 mM Spd + PQ compared to the 0.3 mM Spd + PQ, with no significant difference observed between 0.3 mM Spd and 3 mM Spd, suggesting a concentration dependent autophagy enhancing effect of spermidine in the presence of PQ, as spermidine alone at both concentration did not induce autophagy robustly above control levels and this was supported by the significant increase in autophagy with 3 mM Spd + PQ compared to the 3 mM Spd. Our data is supported by previous findings that show that spermidine supplementation extended lifespan and prevented liver fibrosis by increasing microtubule-associated protein 1S (MAP1S) levels \citep{Yue2017}. Others have reported that oral supplementation (0.3 or 3 mM) in drinking water enhanced autophagy induction leading to cardiac protection and lifespan extension \citep{Eisenberg2016a} and reversed arterial aging \citep{LaRocca2013}. Spermidine exerts its protective effects by modulating autophagy through suppressing the E1A- binding protein p300 (EP300) \citep{Pietrocola2015}.Our western blot data was supported by the immunofluorescence analysis which revealed that GFP-LC3 fluorescence signal was strongly expressed 0.3 mM Spd + PQ, and 3 mM Spd + PQ compared to the PQ treated group (Fig.7.9). In contrast to our LC3-II data, we observed an enhanced p62 expression levels in 3 mM Spd + PQ and 3 mM Spd compared to the control and PQ treated group, but not in the low concentration (0.3 mM Spd + PQ) (Fig.7.8.A.ii). Importantly, PQ treatment did not enhance p62 expression unlike APP. These results are supported by the immunofluorescence analysis with reveal a strong fluorescence intensity signal for p62 in the 3 mM Spd and 3 mM Spd + PQ compared to PQ treated group and control group (Fig.7.10). p62 levels have been shown to increase or decrease during autophagy modulation. For example, p62 levels have been shown to decrease after 4 h of starvation, restored to basal levels, but significantly increased after 8 hours of starvation, and did not return to basal levels \citep{sahani2014}. LAMP2A protein expression was significantly decreased in the PQ treated group, while significantly increased in 0.3 mM Spd, 0.3 mM Spd + PQ and 3 mM Spd + PQ compared to the control group (Fig.7.8.A.iii). Importantly, treatment with spermidine significantly increased LAMP2A expression in 0.3 mM Spd, 0.3 mM Spd + PQ, 3 mM Spd and 3 mM Spd + PQ compared to the PQ treated group. These results suggesting that PQ causes lysosomal damage, leading to defective proteolysis and that spermidine rescues the effect. Defective lysosome are implicated in AD \citep{Nixon2011}, thus, it is safe to assume that PQ might be de-acidifying the lysosome, leading to lysosomal dysfunction. In support of this, rotenone, another pesticide like PQ has been shown to induce lysosomal dysfunction by increasing lysosomal membrane permeability resulting in impaired autophagic flux, and that trehalose, an autophagy inducer, rescued this effect in an \textit{in vivo} model of PD \citep{Wu2015}, supporting both the lysosomal damage by PQ and the rescuing effect by spermidine. In overall, our findings shed light into the mechanisms of spermidine induced neuronal protection in this model system. Due to the importance of the hippocampus in neurodegeneration and also in memory formation, these results are of significant and point towards spermidine as a therapeutic intervention for neurodegenerative diseases.


\section{Cortex region assessment}
\subsection{The effect of treatment intervention on H\&E staining}
Cortex is another region susceptible to pathological changes associated with AD, particularly at the later stages of the disease, thus effects of treatment intervention were assessed in a similar fashion to the hippocampus \citep{Braak1998,Braak1991,Braak2012}. In order to assess overall structural changes of the cortex following treatment intervention, H \& E staining was performed. H\&E staining showed no major abnormal changes in the structural architecture of the cortex upon treatment intervention (Fig.7.11), in agreement with the H\&E data observed hippocampus, suggesting that that PQ-induced toxicity in the brain was not severe to cause structural damage. 

\subsection{The effect of treatment intervention on lipid peroxidation}
Next, we assessed 4HNE.Western blot analysis for 4HNE protein adducts revealed no significant differences in the PQ treated group compared to the control group at 35, 45 and 52 kDa (Fig.7.12.A.i, ii \& iii). At 35 kda, a significant decrease in 4HNE signal was observed in 0.3 mM Spd + PQ group compared PQ treated group (Fig.7.12.A.i). At 45 \& 55 kDa, 4HNE signal was significantly decreased in both spermidine concentrations i.e. 0.3 mM Spd + PQ and 3 mM Spd + PQ compared to the PQ treated group. Additionally, a significant decrease was observed in 0.3 mM Spd + PQ compared to 0.3 mM Spd and in 3 mM Spd compared to 0.3mM Spd at 45 \& 52 Kda. These results are supported by the immunofluorescence data, where a moderately enhanced fluorescence signal for 4HNE was observed in the PQ treated group compared to 0.3mM Spd + PQ and 3mM Spd + PQ (Fig.7.13). In overall, these results suggest that PQ does not induce oxidative stress in the cortex, in contrasting the results observed in the hippocampus, thus suggesting that the cortex is less susceptible to oxidative damage, as it is only affected later in the AD disease progression \citep{lumkwana2017}. Notably, spermidine i.e. 0.3 mM Spd + PQ and 3 mM Spd + PQ brought down lipid peroxidation below PQ and control levels, suggesting that spermidine mediated protection and did so in a concentration dependent manner as evident by the significant decrease in 4HNE signal with 3 mm Spd compared to 0.3 mM Spd, as observed in the hippocampus, again supporting spermidine acts as an antioxidant.

Consistent with the observations in the hippocampus, an enhanced GFAP signal was observed in the PQ treated group compared to all other groups (Fig.7.14), again suggesting that PQ induces astrocyte gliosis as a sign for neuronal injury in this region and that spermidine protects against neuronal damage. In line with these finding, enhanced levels of GFAP were demonstrated in the cortex in a 3xTgAD mice model \citep{Kamphuis2014,Oddo2003}. Because astrogliosis is a hallmark of AD neuropathology \citep{Gotz2001,Grundke-Iqbal1989}, these finding suggest that PQ treatment in 3 weeks induced AD like pathology and that spermidine might have therapeutic potential in AD. In fact, spermidine is part of the ongoing clinical trial study (https://clinicaltrials.gov/ct2/show/NCT02755246). So far, spermidine given in long-term as dietary supplement has been found to be safe and well tolerated in mice and older adults \citep{Schwarz2018}. Moreover, spermidine has been found to improved memory performance in aged adults compared to the placebo group \citep{Wirth2018}, suggesting that spermidine may potentially delay memory loss with age.
Western blot analysis of APP protein expression revealed a trend towards an increase in APP signal in the PQ treated group compared to the control group, but no significant differences were observed (Fig.7.15). In support of our findings, \citet{Chen2012} found no differences in the APP expression in the PQ treated mice compared to the control mice in the cortex after 3 weeks of treatment. Notably, spermidine at both concentrations i.e. 0.3 mM Spd + PQ and 3 mM Spd + PQ significantly decreased APP expression compared to the PQ treated group, again suggesting that, suggesting that spermidine mediated protection. 

In contrast to the observations in the hippocampus, no significant differences were observed in acetylated $\alpha$-tubulin in the 0.3 mM Spd, 0.3 mM Spd + PQ and 3 mM Spd compared to the control and PQ treated group, however, an unexpected decline in acetylated $\alpha$-tubulin below control and PQ group was observed at 3 mM Spd + PQ (Fig.7.16). These results suggest that PQ did not affect acetylated $\alpha$-tubulin in this region and that the low concentration of spermidine in combination with PQ also did not affect microtubules, but the combination of PQ with the highest concentration of spermidine is destabilizing microtubules by mechanisms that are unknown, that might be related to autophagy. 

Our results reveal that LC3 II expression was enhanced spermidine only with the lowest concentration i.e. 0.3 mM Spd + PQ compared to the PQ treated group, but not in the in the PQ treated group itself compared to the control group (Fig.7.17.A.i).These results suggest that autophagy activity was enhanced above basal levels in response to spermidine treatment with the lowest concentration, while PQ exposure alone did not induce autophagy above control levels. The findings were supported by immunofluorescence analysis which revealed that GFP-LC3 signal was enhanced only in the groups 0.3 mM Spd + PQ and 3mM Spd in this region (Fig.7.18). Consistent with these observation, a significant increase in p62 expression was observed in the 0.3 mM Spd + PQ (Fig.7.17.A.ii). Lastly, PQ treatment reduced LAMP2A expression below the control level but not significantly, but spermidine at both concentration increased LAMP2a. These results again suggest that the cortex region is not sensitive to PQ induced lysosomal damage as observed in the hippocampus and that spermidine protects against lysosomal damage. In overall, our findings show that even though the cortex is less impacted by PQ toxicity, spermidine still protects against neuronal damage. 












