\chapter*{Addendum A}\label{addendum}
\addcontentsline{toc}{chapter}{Addendum A}

\section*{Buffers}

\noindent
\textbf{1X Phosphate Buffered Saline (PBS) – 0.1M} \\
Dissolve the following in 1L of water:
\begin{itemize}
\item 16 g NaCl 
\item 0.4 g KCl 
\item 2.88 g Na\textsubscript{2}HPO\textsubscript{4} 
\item 0.48 g KH\textsubscript{2}PO\textsubscript{4} 
\end{itemize}
Adjust pH to 7.4, fill up to the 2L mark with distilled water and sterilize by autoclaving. \\

\noindent
\textbf{RIPA lysis buffer} \\
Dissolve the following:
\begin{itemize}
\item 50 mM Tris-HCl
\item 150 mM NaCl 
\item 1 mM EDTA 
\item 1 \% NP-40 1
\item 0.25 \% Na-deoxycholate 
\end{itemize}
Store at 4 degrees Celsius. \\

\noindent
\textbf{Laemmli’s sample buffer} \\
Mix 850 $\mu$l Solution A and 150 $\mu$l $\beta$-mercaptoethanol. NB: Only mix on the day of use. Solution A:
\begin{itemize}
\item 38 ml dH\textsubscript{2}O
\item 10 ml 0.5 M Tris (pH 6.8)
\item 8 ml glycerol
\item 16 ml 10 \% SDS
\item 4 ml 0.05 \% (w/v) Bromophenol blue
\end{itemize}

\noindent
\textbf{10x Tris-Buffered Saline (TBS)} \\
Dissolve the following in 600 ml dH\textsubscript{2}O:
\begin{itemize}
\item 4.2 g Tris
\item 80 g NaCl   
\item pH adjusted to 7.6 using HCl and adjusted volume to 1 L with dH\textsubscript{2}O
\end{itemize}
\noindent
To make 1x TBST-T, take:
\begin{itemize}
\item 100 ml 10x TBS 
\item 1 ml Tween-20
\item 900 ml dH\textsubscript{2}O
\end{itemize}

\noindent
\textbf{Stripping buffer} \\
Dissolve the following in 800 ml dH\textsubscript{2}O:
\begin{itemize}
\item 15 g Glycine
\item 10 ml 10 \% SDS 
\item 10 ml Tween-20
\end{itemize}
Adjust pH to 2.5 using HCl. \\
 
\noindent
\textbf{1x PBS-A} \\
Dissolve the following in 900 ml of dH\textsubscript{2}O:
\begin{itemize}
\item 8 g NaCl 
\item 0.20 g KCl 
\item 2.20 g Na\textsubscript{2}HPO\textsubscript{4}.7H2O
\item 0.20 g KH\textsubscript{2}PO\textsubscript{4} 
\end{itemize}
Adjust pH to 7.4 with NaOH and fill up to the 1L mark with dH\textsubscript{2}O.\\

\noindent
\textbf{PBS-G (100 mM)} \\
Dissolve:
\begin{itemize}
\item 0.75 g Glycine 
\item 100 ml dH\textsubscript{2}O
\end{itemize}

\noindent
\textbf{1 M MEA buffer} \\
Dissolve in 1 ml 1x PBS-A:
\begin{itemize}
\item 0.113 g MEA powder in 2 ml tube
\end{itemize}

\noindent
\textbf{Saline solution (0.85 \%)} \\
Dissolve 8.5 g NaCl in 1 L dH\textsubscript{2}O and autoclaved for 25 min at 121 degrees celsius and cooled at RT.
Stored at 4 degrees Celsius. \\

\noindent
\textbf{Phosphate buffer (PB) system, pH 7.4} \\
Solution X:
\begin{itemize}
\item 0.2 M disodium hydrogen orthophosphate 
\item Na\textsubscript{2}HPO\textsubscript{4}$\cdot$2H\textsubscript{2}O, 18.69 g in 525 ml dH\textsubscript{2}O 
\end{itemize}
Solution Y:
\begin{itemize}
\item 0.2 M sodium dihydrogen phosphate 
\item Na\textsubscript{2}HPO\textsubscript{4}$\cdot$2H\textsubscript{2}O, 15.60 g in 500 ml dH\textsubscript{2}O 
\end{itemize}
Filter sterilise and store both at 4 degrees Celsius. \\

\noindent
\textbf{0.2 M phosphate buffer (2X PB), store at 4 degrees Celsius}
\begin{itemize}
\item Solution X 202.5 ml 
\item Solution Y 47.5 ml 
\end{itemize}

\noindent
\textbf{0.1 M phosphate buffer (PB), store at 4 degrees Celsius}
\begin{itemize}
\item Solution X 202.5 ml 
\item Solution Y 47.5 ml 
\item dH\textsubscript{2}O 250 ml 
\end{itemize}

\noindent
\textbf{Double strength fix} \\
8\% formaldehyde in ~0.2 M phosphate buffer pH 7.4, make up with 2X PB. \\

\noindent
\textbf{Single strength fix} \\
2.5\% gluteraldehyde, 4\% formaldehyde in 0.1 M PB, make up with 2X PB \\

\noindent
\textbf{2\% reduced osmium (2\% OsO\textsubscript{4}, 1.5\% K\textsubscript{3}Fe(CN)\textsubscript{6}}) \\
Mix equal volumes of aqueous 4\% OsO\textsubscript{4} and 3\% K\textsubscript{3}Fe(CN)\textsubscript{6}, just before use. \\

\noindent
\textbf{TCH} \\
1\% Thiocarbohydrazide (TCH) solution; make fresh during the reduced osmium incubation.
\begin{itemize}
\item Add 0.1 g thiocarbohydrazide (Sigma) to 10 ml dH\textsubscript{2}O, incubate for 1 h, 60 degrees Celsius 
\item Swirl gently every 10 minutes to facilitate dissolving
\item Filter through a 0.22 $\mu$m Millipore syringe filter right before use
\end{itemize}

\noindent
\textbf{Walton’s lead aspartate (Walton, 1979)} \\
Aspartic acid 0.03 M pH 3.8 stock:
\begin{itemize}
\item Make up aspartic acid 0.03 M (L-asp OK); pH to 3.8 with 1 M KOH to help dissolve the aspartic acid
\item Store at 4 degrees Celsius up to 2 months
\end{itemize}
For 10 mL lead aspartate:
\begin{itemize}
\item Dissolve 0.066 g lead nitrate in 10 mL room temperature 0.03 M pH 3.8 aspartic acid stock, and pH to 5.5 dropwise with 1 M KOH, checking pH with paper strips (1-2 drops at a time from a glass pipette; more at once will cause precipitation), while swirling to mix (do not use magnetic stirrer, the slightest bumps cause precipitation, even at lower pH)
\item Incubate in glass vial for 30 min, 60 degrees Celsius (no precipitate should form)
\end{itemize}
For 20 ml, add 0.132 lead nitrate to 18 ml of 0.03 M aspartic acid. Takes 20-25 drops of 1 M KOH to pH 4.5. Then ~4 drops to pH 5.5. \\

\noindent
\textbf{100\% dry ethanol} 
\begin{itemize}
\item Place ~20\% volume of sodium sulphate on a metal tray, spread out and bake o/n, 60 degrees Celsius, to remove moisture
\item Transfer sodium sulphate to a bottle, add 99-100\% ethanol until it’s brim full, shake, and leave to settle
\end{itemize}

\noindent
\textbf{Durcupan ACM} \\
Make up as Epon; with a stirrer bar, add each component on top of the previous. Gets quite viscous, does not mix very well, use flat bottomed container.
\begin{itemize}
\item 11.4 g part A (Red cap, epoxy resin)
\item 10 g part B (Blue cap, 964 hardener)
\item 0.3 g part C (Yellow cap, 964 accelerator)
\item 0.05-0.1 g part D (Green cap, dibutyl phthalate) (0.05-0.1 g range, since it is a small volume difficult to measure)
\end{itemize}


